Describing vocalizations in young children: A big data approach through citizen science annotation

### 2021-03-08 202010_jslhr/paper.Rmd
attempts at increasing reproducibility

```{r setup, include = FALSE}
library(groundhog)
groundhog.day="2021-02-23"
pkgs=c('papaja','tidyverse','dplyr','ggplot2','caret','scales','kableExtra','rel','ggpubr','lme4','rmarkdown')
groundhog.library(pkgs, groundhog.day)

@@

#document session info
capture.output(sessionInfo(),file="paper-lastknit_session_info.txt")

@@

The first step we took before beginning the annotation process was the identification of children's vocalizations within day-long recordings. We did this automatically, using the LENA&reg; proprietary software [@xu2008signal]. Specifically, the LENA&reg; software attempts to assign segments of speech either to the key child (the one wearing the recorder), or to one of 15 other categories in the child’s environment (e.g., Female-Adult, TV). Key child labels have a precision of about 60% and a recall of about 50% [@cristia2020thorough]. These stretches of audio assigned to the key child can contain cries, vegetative sounds, and linguistic vocalizations, as well as interstitial pauses. We refer to them as *segments*, to highlight the fact that they are stretches of audio segmented out as belonging to the key child, but they may not be individual vocalizations.

@@

Coders were also given a "Don’t Mark" option, which they were instructed to use if the segment did not sound like a segment made by the target child, or if there is any overlapping speech or other noise in the background which could affect acoustic analyses. This category is broader than the "Junk" category used by Zooniverse annotators, which is explained in the next section.

@@

resampling=matrix(NA,nrow=50,ncol=6)
colnames(resampling)<-c("lp_r_all","lp_r_as","lp_r_lr","cp_r_all","cp_r_as","cp_r_lr")
for(i in 1:50){
  sel_seg=NULL
  for(thischi in levels(data_all$ChildID)) sel_seg<-c(sel_seg,as.character(data_all$segmentId_DB[sample(data_all$segmentId_DB[data_all$ChildID==thischi],100)]))

  sampling=data_all[as.character(data_all$segmentId_DB) %in% as.character(sel_seg),]

@@

   resampling[i,"cp_r_all"]=cor.test(thistab$z_cp,thistab$l_cp)$estimate
  resampling[i,"cp_r_as"]=cor.test(thistab$z_cp[thistab$Diagnosis=="AngelmanSyndrome"],thistab$l_cp[thistab$Diagnosis=="AngelmanSyndrome"])$estimate
  resampling[i,"cp_r_lr"]=cor.test(thistab$z_cp[thistab$Diagnosis!="AngelmanSyndrome"],thistab$l_cp[thistab$Diagnosis!="AngelmanSyndrome"])$estimate
 }
myr=colMeans(resampling)
mycortab=rbind(mycortab,cbind(myr[c("lp_r_as" ,"lp_r_lr","lp_r_all")],myr[c("cp_r_as" ,"cp_r_lr","cp_r_all")]))
rownames(mycortab)[7:9]<-c("100 seg AS","100 seg LR","100 seg all")
for(i in 1:dim(mycortab)[1]) for(j in 1:dim(mycortab)[2]) mycortab[i,j]<-printr(as.numeric(as.character(mycortab[i,j])))

>>>>

```{r setup, include = FALSE}

library(groundhog)
groundhog.day="2021-02-23"
#groundhog.library('papaja', groundhog.day) #NOTE! THIS IS A POINT OF POTENTIAL NON-REPRODUCIBILITY
library(papaja) #NOTE!
groundhog.library('tidyverse', groundhog.day)
groundhog.library('dplyr', groundhog.day)
groundhog.library('ggplot2', groundhog.day)
groundhog.library('rmarkdown', groundhog.day)
groundhog.library('caret', groundhog.day)
groundhog.library('scales', groundhog.day)
groundhog.library('kableExtra', groundhog.day)
groundhog.library('rel', groundhog.day)
groundhog.library('ggpubr', groundhog.day)
groundhog.library('lme4', groundhog.day)
groundhog.library('e1071', groundhog.day)

@@

#document session info
capture.output(sessionInfo(),file="lastknit_session_info.txt")

@@

The first step we took before beginning the annotation process was the identification of children's vocalizations within day-long recordings. We did this automatically, using the LENA&reg; proprietary software [@xu2008signal], with versions ranging from LENA Pro 3.5 to LENA HUB 3.3 to 4.0. In broad terms, the LENA&reg; software attempts to assign segments of speech either to the key child (the one wearing the recorder), or to one of 15 other categories in the child’s environment (e.g., Female-Adult, TV). Key child labels have a precision of about 60% and a recall of about 50% [@cristia2020thorough]. These stretches of audio assigned to the key child can contain cries, vegetative sounds, and linguistic vocalizations, as well as interstitial pauses. We refer to them as *segments*, to highlight the fact that they are stretches of audio segmented out as belonging to the key child, but they may not be individual vocalizations.

@@

Coders were also given a "Don’t Mark" option, which they were instructed to use if the segment did not sound like a segment made by the target child, or if there is any overlapping speech or other noise in the background which could affect acoustic analyses. This category is broader than the "Junk" category used by Zooniverse annotators, which is explained in the next section. Training materials for laboratory coders are available from @hamrick2021si.

@@

resampling=matrix(NA,nrow=50,ncol=6)
colnames(resampling)<-c("lp_r_all","lp_r_as","lp_r_lr","cp_r_all","cp_r_as","cp_r_lr")

for(i in 1:50){
  sel_seg=NULL

  #the next line samples 100 voc IDs from each child
  for(thischi in levels(factor(data_all$ChildID))) sel_seg<-c(sel_seg,as.character(sample(data_all$segmentId_DB[data_all$ChildID==thischi],100)))

  #generate a subset using those voc IDs
  sampling=data_all[as.character(data_all$segmentId_DB) %in% as.character(sel_seg),]

@@

   resampling[i,"cp_r_all"]=cor.test(thistab$z_cp,thistab$l_cp)$estimate
  resampling[i,"cp_r_as"]=cor.test(thistab$z_cp[thistab$Diagnosis=="AngelmanSyndrome"],thistab$l_cp[thistab$Diagnosis=="AngelmanSyndrome"])$estimate
  resampling[i,"cp_r_lr"]=cor.test(thistab$z_cp[thistab$Diagnosis!="AngelmanSyndrome"],thistab$l_cp[thistab$Diagnosis!="AngelmanSyndrome"])$estimate
}

myr=colMeans(resampling)
mycortab=rbind(mycortab,cbind(myr[c("lp_r_as" ,"lp_r_lr","lp_r_all")],myr[c("cp_r_as" ,"cp_r_lr","cp_r_all")]))
rownames(mycortab)[7:9]<-c("100 seg AS","100 seg LR","100 seg all")
for(i in 1:dim(mycortab)[1]) for(j in 1:dim(mycortab)[2]) mycortab[i,j]<-printr(as.numeric(as.character(mycortab[i,j])))
